\pdftitle

### 2017-05-16 maxNt.tex
comments on intro

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-16T01:37:28+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\section{Implicit assumptions in the maximum-entropy method}

The \me\ method is used in neuroscience blahblah***

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-16T16:44:08+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

%\section{Implicit assumptions in the maximum-entropy method}
\section{Introduction}

Recent advances in electrophysiological techniques allow to record from
large\mynote{\enquote{from large} or just \enquote{large}? But is the
  largeness relevant in our paper?} population of neurons [\cite]. The recorded
neurons are usually picked out from a specific brain area according to an
unknown process, and from their observation in relation to stimuli or
behavioral task, we strive for understanding the mechanism behind neuronal
coding\mynote{LM still don't know what people mean by this, can we find an
  unambiguous term or rephrase?}. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that
area.\mynote{This assumption says that from the sample we can learn about
  the population. The relation of population activity with stimuli or
  behaviour is a separate problem, so \enquote{this is} doesn't really fit...}

Huge amounts of parallel recordings from hundreds of neurons, available
today, are accompanied by the statistical challenges to be employed for
shedding light on the mechanism behind neuronal coding. The principle of
\me\ was proposed as a way to overcome these challenges by constructing a
full description of the neuronal firing patterns. The \me\ method employs
only first and second order statistics of the representative random sample
to construct a \enquote{maximally noncommittal} \cite{jaynes1963}
probability distribution of the firing patterns [\cite]. \mynote{LM:
  \enquote{noncommittal} doesn't mean anything to me to be honest, even if
  Jaynes used that term. I would like to openly say this, backed up by
  references, as done some paragraphs below.\\It seems they have used \me\
  for other purposes too, sometimes unclear ones. And with all kinds of
  constraints. So we shouldn't be too specific here in relation to purpose
  and constraints. I'd rather give references and the readers can form
  their own ideas about its use.}

Using the pairwise \me\ models many studies investigated the questions such
as, which level of interaction\mynote{ambiguous word} (pairwise or higher-order)
between neurons is suffiecient to explain the observed experimental data
[\cite]? Or how collective behavior of neurons can be related to stimuli or
behavioral tasks [\cite]? add more **

Here we show that there is a quandary in applying \me\ to a representative
random sample of neurons to generate a maximally noncommital distribution
for that sample.

The quandary is this. Assume that our sample of neurons is
representative of some population. If we assign a \me\ distribution to the
sample, then we cannot assign a \me\ distribution to the full population.
Vice versa, If we assign a \me\ distribution to the full population, then
we cannot assign a \me\ distribution to the sample. This impossibility
holds at least for \me\ distribution with moment constraints, and even if
the orders of the moments constrained in the sample and in the full
population are different.
